Dissertation

### 2024-10-20 Manuscript/pre_sections/pre_html2.qmd
re-render after all ugs revision changes again

<div class="submitted">
Submitted to the faculty of the Graduate School<br>
in partial fulfillment of the requirements<br>
for the degree<br>
Doctor of Philosophy<br><br>
in the Cognitive Science Program and<br>
Department of Psychological and Brain Sciences,<br>
Indiana University<br>
October 2024
</div>

@@

<div class="copyright">&copy; 2024 <br><br> Thomas E. Gorman </div>

>>>>

<div class="submitted">
Submitted to the faculty of the Graduate School<br>
in partial fulfillment of the requirements<br>
for the degree<br>
Doctor of Philosophy<br>
in the Cognitive Science Program and<br>
Department of Psychological and Brain Sciences,<br>
Indiana University<br>
October 2024
</div>

@@

<div class="copyright"> Copyright &copy; 2024 <br><br> Thomas E. Gorman </div>

### 2024-10-20 Sections/pre_sections/pre_pdf.qmd
re-render after all ugs revision changes again

\begin{centering}
\LARGE
{The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach}

\vspace*{1.5cm}

\LARGE
{Thomas E. Gorman}

\vspace{16.5cm}

Submitted to the faculty of the University Graduate School in partial fulfillment of the
requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
Sciences and the Cognitive Science Program, Indiana University
Indiana University

@@

\pagenumbering{gobble}

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.
\vspace{4cm}

\
\_____________________________  Robert L. Goldstone, PhD
\vspace{2.5cm}
\
\
\_____________________________  Robert Nosofsky, PhD
\vspace{2.5cm}
\
\_____________________________  Peter Todd, PhD
\vspace{2.5cm}
\
\_____________________________  Mike Jones, PhD

@@

@2024 \\
\vspace{1cm}

>>>>

{THE ROLE OF VARIABILITY IN LEARNING GENERALIZATION: A COMPUTATIONAL MODELING APPROACH}

\vspace{5\baselineskip}

{Thomas E. Gorman}

\vspace{10.5cm}

Submitted to the faculty of the Graduate School \\
in partial fulfillment of the requirements \\
for the degree \\
Doctor of Philosophy \\
in the Cognitive Science Program and \\
Department of Psychological and Brain Sciences, \\
Indiana University \\
October 2024

@@

\pagenumbering{gobble}
\end{centering}

\newpage
\pagenumbering{roman}
\setcounter{page}{2}
\begin{center}

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.
\end{center}
\vspace{1cm}
\
Doctoral Committee
\vspace{1cm}

\begin{flushright}
\underline{\hspace{5cm}} \\
Robert L. Goldstone, Ph.D.
\vspace{2cm}

\underline{\hspace{5cm}} \\
Robert M. Nosofsky, Ph.D.
\vspace{2cm}

\underline{\hspace{5cm}} \\
Peter M. Todd, Ph.D.
\vspace{2cm}

\underline{\hspace{5cm}} \\
Michael N. Jones, Ph.D.
\end{flushright}

\
May 28th, 2024

@@

Copyright @ 2024 \\
\vspace{.5cm}
